---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Load package
```{r setup}
library(ColonyFileGenerator)
```


# Specify samples
These are vectors with the sample names that you want to use for each category in Colony.
Note: If the sex of potential parental samples are not known, you can include them in BOTH the mother and father lists.
```{r}
# These are the vectors with the sample names that you want to use for each catagory in Colony
father.id <- c("1A","1C","1E","1G") # Potential father samples
mother.id <- c("1B","1D","1F","1H") # Potential mother samples
offspring.id <- c("1I","1J","1K","1L","1M","1N","1O","1P","1Q","1R","1S","1T","1U","1V","1W","1X","1Y","1Z","2A","2B","2C","2D","2E","2F","2G","2H","2I","2J","2K","2L","2M","2N","2O","2P","2Q","2R","2S","2T","2U","2V","2W","2X")
```

# Read in VCF file
This is where you specify and load your filtered VCF.
Here we demonstrate with example data included in the package.
```{r}
system.file("extdata", "example.vcf", package = "myfirstpackage")
vcf.file <- "./Data/example.vcf"
vcf.df <- processVCF(vcf.file)
```

# Filter samples with missing data
Here you can filter out samples with excessive missing data
Note: Colony will not run if you have samples with NO data, so it is recommended to filter with at least a 99% threshold.
```{r}
vcf.cut <- filterMissVCF(vcf.df, perc.missing = 50)
```

# Write the Colony output file
Here you create the actual data file that is used as an input in the software colony (https://www.zsl.org/science/software/colony).
There are many parameters you can set, please check the function documentation (?writeColonyFile) for more details.
```{r}
writeColonyFile(colony.run.name = "colony_run1",
                out.path = "./output/",
                offspring.id = offspring.id,
                father.id = father.id,
                mother.id = mother.id,
                vcf.input.df = vcf.cut)
```


